Autoignition of Methyl Valerate at Low to Intermediate Temperatures and Elevated Pressures in a Rapid Compression Machine

### 2017-06-27 methyl-valerate.tex
Updates for ignition delay

It can be seen from \cref{fig:ignition-delays} that the ignition delays for the
\(\phi=0.25\text{ and } 0.5\) mixtures do not show an NTC region of the ignition
delay for both of the pressures studied in this work. However, the $\phi=1.0$
mixture shows an NTC region at $P_C=\SI[number-unit-product={\ }]{30}{\bar}$
between approximately \SIlist{720;800}{\K}, with measured first-stage ignition
delays at \SIlist{734;757}{\K}. In addition, the $\phi=2.0$ mixture shows an NTC
region of ignition delay at \SI{15}{\bar} from approximately
\SIrange{720}{775}{\K}, with measured first-stage ignition delays between
\SIlist{720;750}{\K}.

\begin{figure}[htb]
    \centering
    \resizebox{\linewidth}{!}{\input{figures/ignition-delays.pgf}}
    \caption{Ignition delays of MV as a function of inverse temperature. Filled
    points are the overall ignition delays and hollow points are the first stage
    ignition delays. a) \SI{15}{\bar}. b) \SI{30}{\bar}}
    \label{fig:ignition-delays}
\end{figure}

\Cref{fig:pressure-traces} shows the pressure traces for selected experiments at
\(\phi=1.0\), \(P_C =\SI[number-unit-product={\ }]{30}{\bar}\). The three
reactive pressure traces shown are at the low-temperature end of the NTC (blue,
\SI{700}{\K}), one case with two-stage ignition (orange, \SI{734}{\K}), and one
case near the high-temperature limit of the NTC region (green, \SI{775}{\K}).
Also shown is the non-reactive pressure trace for the \SI{700}{\K} case (red).
By comparing the \SI{700}{\K} pressure trace with the non-reactive pressure
trace, it can be seen that there is substantial heat release prior to main
ignition as measured by the deviation of the reactive pressure trace from the
non-reactive trace. However, there is only one peak in the time derivative of
the pressure, so no first-stage ignition delay is defined for this case. It can
also be seen in \cref{fig:pressure-traces} that the \SI{775}{\K} case shows some
heat release prior to ignition, although again there is only one peak in the
time derivative of the pressure. Furthermore, the heat release at \SI{775}{\K}
appears to be more gradual than at the lowest temperature.

\begin{figure}[htb]
    \begin{minipage}[t]{0.48\textwidth}
        \centering
        \resizebox{\linewidth}{!}{\input{figures/pressure-traces.pgf}}
        \caption{Selected pressure traces around the NTC region of ignition delay for $\phi=1.0$}
        \label{fig:pressure-traces}
    \end{minipage}\hfill%
    \begin{minipage}[t]{0.48\textwidth}
        \centering
        \resizebox{\linewidth}{!}{\input{figures/simulation-comparison.pgf}}
        \caption{Comparison of experimental and simulated results for $\phi=1.0$}
        \label{fig:simulation-comparison}
    \end{minipage}
\end{figure}

>>>>

It can be seen from \cref{fig:ignition-delays} that the ignition delays for the \(\phi=0.25\text{
and } 0.5\) mixtures do not show an NTC region of the ignition delay for both of the pressures
studied in this work. However, the $\phi=1.0$ mixture shows an NTC region at
$P_C=\SI[number-unit-product={\ }]{30}{\bar}$ between approximately \SIlist{720;800}{\K}, with
measured first-stage ignition delays at \SIlist{733;757}{\K}. In addition, the $\phi=2.0$ mixture
shows an NTC region of ignition delay at \SI{15}{\bar} from approximately \SIrange{720}{780}{\K},
with measured first-stage ignition delays between \SIlist{720;750}{\K}.

\begin{center}
    \captionsetup{type=figure}
    \includegraphics{figures/ignition-delays.pdf}
    \caption{Ignition delays of MV as a function of inverse temperature. Filled
    points are the overall ignition delays and hollow points are the first stage
    ignition delays. a) \SI{15}{\bar}. b) \SI{30}{\bar}}
    \label{fig:ignition-delays}
\end{center}

\Cref{fig:pressure-traces}a shows the pressure traces for selected experiments at \(\phi=1.0\),
\(P_C =\SI[number-unit-product={\ }]{30}{\bar}\). The three reactive pressure traces shown are at
the low-temperature end of the NTC (blue, \SI{700}{\K}), one case with two-stage ignition (orange,
\SI{733}{\K}), and one case near the high-temperature limit of the NTC region (green, \SI{774}{\K}).
Also shown is the non-reactive pressure trace for the \SI{700}{\K} case (red). By comparing the
\SI{700}{\K} pressure trace with the non-reactive pressure trace, it can be seen that there is
substantial heat release prior to main ignition as measured by the deviation of the reactive
pressure trace from the non-reactive trace. However, there is only one peak in the time derivative
of the pressure, so no first-stage ignition delay is defined for this case. It can also be seen in
\cref{fig:pressure-traces}a that the \SI{775}{\K} case shows some heat release prior to ignition,
although again there is only one peak in the time derivative of the pressure. Furthermore, the heat
release at \SI{775}{\K} appears to be more gradual than at the lowest temperature.

\begin{center}
    \captionsetup{type=figure}
    \includegraphics[width=\textwidth]{figures/pressure-traces.pdf}
    \caption{Selected pressure traces around the NTC region of ignition delay.
    a) \(\phi=1.0\) b) \(\phi=2.0\)}
    \label{fig:pressure-traces}
    % \begin{minipage}[t]{0.48\textwidth}
    %     \centering
    %     \resizebox{\linewidth}{!}{\input{figures/simulation-comparison.pgf}}
    %     \caption{Comparison of experimental and simulated results for $\phi=1.0$}
    %     \label{fig:simulation-comparison}
    % \end{minipage}
\end{center}

A similar trend can be observed in \cref{fig:pressure-traces}b for \(\phi=2.0\) at \(
